\documentclass[../main.tex]{subfiles}

\begin{document}

\begin{thebibliography}{999}

% \bibitem{template-00}
%   Author Surname, Author Initial.
%   (Year published).
%   \emph{Title}.
%   [online]
%   Available at:
%   \url{}
%   [Accessed date]

\bibitem{keane-17}
  Keane A. J., S\'obester A., Scanlan J. P.
  (2017).
  \emph{Small Unmanned Fixed-wing Aircraft Design: A Practical Approach}.
  Chichester: John Wiley \& Sons.

\bibitem{kroo-86}
Kroo, I.
(1986).
\emph{Propellor-wing interaction for minimum induced loss}.

\bibitem{pooneh-18}
  Pooneh A.
  (2018).
  \emph{Computational Study of Propeller-Wing Aerodynamic interaction}.

\bibitem{xflr-19}
  XFLR.
  (2019).
  \emph{XFLR}.

\bibitem{airfoil-tools-19}
  AIRFOIL TOOLS.
  (2019).
  \emph{Airfoil Tools}.
  [online]
  Available at:
  \url{http://airfoiltools.com/}
  [Accessed 19th December 2019]

\bibitem{spotter-19}
  SPOTTER.
  (2019).
  \emph{SPOTTER}.
  [online]

\bibitem{raymer-89}
  Raymer, D. P.
  (1989).
  \emph{Aircraft Design: A Conceptual Approach}.
  1st edition.
  Washington: American Institute of Aeronautics and Astronautics.

\bibitem{towell-19}
  Towell, K.
  (2019).
  \emph{Professor}.
  [interview]
  (November 2019).

\bibitem{sadraey-13}
  Sadraey, M. H.
  (2013).
  \emph{Aircraft Design: A Systems Engineering Approach}.
  1st edition.
  New Hampshire, USA: Wiley.

% Uncited references

\bibitem{bresloff-18}
  Bresloff, P. N.
  (2018).
  \emph{SESA3026 Aircraft Structural Design}.
  Southampton: University of Southampton.

\bibitem{de-kat-17}
  De-Kat, D. R.
  (2017).
  \emph{SESA2025 Mechanics of Flight}.
  Southampton: University of Southampton.

\bibitem{goud-14}
  Goud, R. K.
  (2014).
  \emph{Stress Analysis of the Landing Gearwell bems and damage calculation due to landing cycles}.

\bibitem{solidworks-19}
  SOLIDWORKS.
  (2019).
  \emph{Solidworks}.

\bibitem{torenbeek-76}
  Torenbeek, E.
  (1976).
  \emph{A Synthesis of Subsonic Airplane Design}.
  1st edition.
  Rotterdam: Delft University Press.

\end{thebibliography}

\end{document}
